Global study of well-being and internet adoption | Online analysis supplement

### 2021-11-29 03-model-estimate.Rmd
fix data and setting hmc options

# MCMC settings
options(brms.backend = "cmdstanr")
hmc <- list(
  chains = 4,
  cores = 4,
  threads = 3,
  iter = 2000, 
  warmup = 1000,
  refresh = 50,
  adapt_delta = .90, 
  max_treedepth = 10
)
```

@@

# Indicate unique ITU values for MV model
dat <- dat %>% 
  # Unique values exist for each country-year
  group_by(region, country, year) %>% 
  mutate(itu = 1:n() == 1) %>% 
  ungroup()
```

>>>>

# MCMC settings
ncores <- min(parallel::detectCores(), 12)
nchains <- 4
options(brms.backend = "cmdstanr")
hmc <- list(
  chains = nchains,
  cores = nchains,
  threads = ncores %/% nchains,
  iter = 2000, 
  warmup = 1000,
  refresh = 50,
  adapt_delta = .90, 
  max_treedepth = 10
)
```

@@

# Indicate unique ITU values for MV model
dat <- dat %>% 
  # Unique values exist for each country-year, but must be given for each
  # outcome
  group_by(region, country, year, cause) %>% 
  mutate(itu = 1:n() == 1) %>% 
  ungroup()
```
